One exact and one random sampling method to assess the reliability of inferences from network enrichment analysis

### 2018-05-06 doc/genesetdp.tex
Now compiling.

To illustrate the $p$~value calculation procedure we plotted the score distributions N(s) for a query size of 10, 20 and 30 genes in Figure \ref{fig:score_dist}, using GeneSetDP.

\begin{figure}[htb]
		\begin{center}
    \begin{array}[ccc]
      \includegraphics[with=4.5cm]{figures/score_distribuition.png &
      \includegraphics[with=4.5cm]{figures/score_distribuition.png} &
      \includegraphics[with=4.5cm]{figures/score_distribuition.png} \\
      $Q=10$ & $Q=20$ & $Q=30$
    \end{array}
		\end{center}
\caption{{\bf Score distribution of a query size of 10, 20 and 30 genes against the ``Glycolysis/Gluconeogenesis'' pathway.} GeneSetDP enables us to calculate the full score distribution for a query of a given size, $Q$, i.e. how many ways one can reach a certain score when adding up the scores for $Q$ genes.}
  \label{fig:score_dist}
FIXME: update these figures.
\end{figure}

@@

\begin{figure}[htb]
  \begin{center}
  \begin{array}[ccc]
    \includegraphics[with=4.5cm]{figures/calibration.png &
    \includegraphics[with=4.5cm]{figures/calibration.png} &
    \includegraphics[with=4.5cm]{figures/calibration.png} \\
    $Q=10$ & $Q=20$ & $Q=30$
  \end{array}
  \caption{{\bf Calibration of GeneSetDP.} We selected 10000 random sets of 10, 20 and 30 genes from the investigated genome definition and calculated their $p$ values with GeneSetMC and GeneSetDP against the ``Glycolysis/Gluconeogenesis'' pathway. To test the $p$~values uniformity we plotted them against their normalized rank. We also added the calibration curve of BinoX, evaluated on the same random sets.}
  \label{fig:calibration}
\end{figure}

>>>>

To illustrate the $p$~value calculation procedure, we plotted the score distributions $N(s)$ for a query size of 10, 20 and 30 genes in Figure \ref{fig:score_dist}, using GeneSetDP.

\begin{figure}[htb]
	\begin{center}
    \begin{tabular}{c@{}c@{}c}
      \includegraphics[width=5cm]{figures/score_distribuition.png} &
      \includegraphics[width=5cm]{figures/score_distribuition.png} &
      \includegraphics[width=5cm]{figures/score_distribuition.png} \\
      $Q=10$ & $Q=20$ & $Q=30$ \\
    \end{tabular}
	\end{center}
  {\em FIXME: update these figures.}
  \caption{{\bf Score distribution of a query size of 10, 20 and 30 genes against the ``Glycolysis/Gluconeogenesis'' pathway.} GeneSetDP enables us to calculate the full score distribution for a query of a given size, $Q$, i.e. how many ways one can reach a certain score when adding up the scores for $Q$ genes.}
  \label{fig:score_dist}
\end{figure}

@@

\begin{figure}[htb]
  \begin{center}
    \begin{tabular}{c@{}c@{}c}
      \includegraphics[width=5cm]{figures/calibration.png} &
      \includegraphics[width=5cm]{figures/calibration.png} &
      \includegraphics[width=5cm]{figures/calibration.png} \\
      $Q=10$ & $Q=20$ & $Q=30$
    \end{tabular}
  \end{center}
  \caption{{\bf Calibration of GeneSetDP.} We selected 10000 random sets of 10, 20 and 30 genes from the investigated genome definition and calculated their $p$ values with GeneSetMC and GeneSetDP against the ``Glycolysis/Gluconeogenesis'' pathway. To test the $p$~values uniformity we plotted them against their normalized rank. We also added the calibration curve of BinoX, evaluated on the same random sets.}
  \label{fig:calibration}
\end{figure}
